Exception Handling Bug Hazards in Android

### 2016-04-20 SPRINGER_JOURNAL/msr_journal.tex
addressing the motivations behind research questions

\textcolor{red}{As previously mentioned, the goal of this work is to obtain a thorough understanding of common exception handling \emph{bug hazards} that app developers face. In the first phase of this work, we conducted a mining study which identified common exception handling bug hazards in app development.
 In the second phase of this work, we set up an exploratory qualitative investigation and surveyed Android developers on how they perceive the bug hazards detected in the mining study. The scope of our study is GitHub---using our GHTorrent database~\cite{Gousi13}, we aimed our survey at developers from Android projects available in GitHub for which issues were mined during the first phase of this study.}

@@

To make the analysis easier, we further refine this question into sub-questions, as follows. To investigate whether the development of exception handling code is a daily concern for developers or it is something that developers face seldom and for that reason do not care much, the following subquestions are added: \emph{How often do developers handle exceptions?} \emph{How often do developers throw exceptions?} And, to check if the Java EH best practices, available in literature, are used in practice and to investigate if any Android-specific EH best practice are used by developers, the following subquestion is added  subquestion: \emph{Do developers know about Java EH best practices and/or Android specific EH best practices?}

The subsequent research questions focus on the developers' perspectives about the main bug hazards found during the mining study, more specifically:

@@

We address these questions by presenting a set of code snippets in which the bug hazards are present, asking developers what they would do when faced with such scenarios.

Our last research question addresses
whether the exception handling code helps with the development of robust Android applications, and what developers usually do to prevent apps from crashing:

>>>>

\textcolor{red}{As previously mentioned, the goal of this work is to obtain a thorough understanding of common exception handling \emph{bug hazards} that app developers face. In the first phase of this work, we conducted a mining study which identified common exception handling bug hazards in app development.
 In the second phase of this work, we set up an exploratory qualitative investigation and surveyed Android developers on how they perceive the bug hazards detected in the mining study. The scope of our study is GitHub---using our GHTorrent database~\cite{Gousi13}, we aimed our survey at developers from Android projects available in GitHub for which issues were mined during the first phase of this study. Next sections detail this exploratory qualitative investigation.}

@@

\textcolor{red}{To make the analysis easier, we further refine this question into sub-questions, as follows. To investigate whether the development of exception handling code is a daily concern for developers or it is something that developers rarely face and for that reason do not care much, the following subquestions are added: \emph{How often do developers handle exceptions?} \emph{How often do developers throw exceptions?} And, to evaluate developers knowledge concerning EH best practices, we also investigated: \emph{Do developers know about Java EH best practices and/or Android specific EH best practices?}}

The subsequent research questions focus on the developers' perspectives about the main bug hazards found during the mining study. We address these questions by presenting a set of code snippets in which the bug hazards are present, asking developers what they would do when faced with such scenarios. The questions related to bug hazards are as follows:

@@

\textcolor{red}{Our last research question addresses whether the exception handling code helps with the development of robust Android applications, and what developers usually do to prevent apps from crashing. The motivation behind this question was to discover common practices for dealing with uncaught exceptions and to acess developers opinion about the role of the exception handling mechanism in the development of robust apps. Hence, the last question is as follows:}
